---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# bananagramr

The goal of bananagramr is to explore whether our bags of bananagrams would have
been fine if we just randomly split them.

# installing bananagramr

```{r install, eval = FALSE}

#install.packages("devtools")

devtools::install_github("njtierney/bananagramr")

```

## The story

I was at a party and we combined two packets of bananagrams to play a big game, but then when we came to putting them back together we wanted to just randomly split them. I understood that this should be fine, but I wanted to be sure. Naturally, everyone was super thrilled when I demanded that we count up all the tiles and record the number in each letter for each of the randomly chosen tiles.

I promised my friends that I'd write about this process, and I like writing R packages as analyses, so this seemed like a good idea. The data can be accessed using

```{r use}
library(bananagramr)

dat_bananagram
```

